### 2021-06-28 src/paper/literature_review.tex
Create arXiv preprint v2. (#3)
Move all comments in the references to comment fields so they are not printed as part of the bibliography.

\section{Literature Review}
\label{sec:literature_review}

We build on two strands of literature: Recent extensions of the epidemiological SEIR
model and agent-based simulation models.

>>>>

\subsection{Literature Review}
\label{sec:literature_review}

We build on two strands of literature: Recent extensions of the epidemiological SEIR
model and agent-based simulation models.\comment[id=K]{Write a sentence about the
\href{https://www.itwm.fraunhofer.de/de/presse-publikationen/presseinformationen/2021/2021-06-22_Dritte_Welle_Starker-Effekt-von-Schnelltests-an-Schulen.html}{Frauenhofer
paper} coming to similar conclusions: }
